Gravitational Lens Modelling of Flux Ratio Anomalous System B1555+375

### 2015-02-12 papers/B1555_EdgeOn/B1555_letter.tex
fix typo

\shorttitle{Gravitational Lens Modeling of Flux Ratio Anomalous System B1555+375}
\shortauthors{TBD}

@@

\title{Gravitational Lens Modeling of Flux Ratio Anomalous System B1555+375}
\author{TBD}

@@

\section{Lens Modeling}
To model B1555+375, we use the lens modeling code {\tt glafic}
\citep{Oguri}.  The inputs to the model are the observed image positions
and flux densities measured by the radio observations of \citet{Marlow}.
These authors present a singular isothermal ellipsoid (SIE) model that
provides the first fit to the image positions but
does not reproduce the strong flux ratio anomaly between components A and B.
(see Fig.6, Table 2 \& 3 in \citet{Marlow}). In K-band
image (Fig. 1, left), a recognizable edge-on disk is lie in the center
with position angle $~10$ degree. With this information, we model
B1555+375 with two models. The first model consists of an SIE bulge
and an exponential edge-on disk (SIE+Expdisk). The second model
consists of two SIE mass profiles (2-SIE), for bulge and disk
respectively. We assume that the lens galaxy has $z_{l}=0.5$ and the source has $z_s=1.5$. The full best-fit parameters are shown in Table 1. Both
of these models predict fairly matched results with the radio
observation. The comparison of observation and SIE+Expdisk result is
in Figure 2, Table 2 \& 3.
%These authors present a singular isothermal ellipsoid (SIE) model that
%provides an excellent fit to the image positions (?? IS THIS TRUE?--NO we get a better model result)

@@

Base on the fact that surface brightness is sensitive to perturbations in gravitational potential, flux ratio anomalies has been shown as one of the most effective methods to detect substructures \citep{Dalal2002} (more ref). Until now there are a dozen(?) known flux ratio anomalous systems and the number must increase in the future survey. Radio data provides reliable positions and fluxes of source for constraint and modeling because it avoids the problem of severe extinction and micro lensing from stars. On the other hand, optical or near infrared imaging also gives useful information about the lensing system. In the previous paper of SHARP, \citet{SHARP12} show that high resolution IR imaging improves the lens modeling. The lack of knowledge about lens galaxy, e.g. modeling with radio data alnog, may lead to an improper lens model.

@@

In sec. 2, we present new lens models of B1555+375 with a bulge and an edge-on disk. Our models better match to the radio image positions than in \citet{Marlow} and also explain the flux ratio anomaly between components A and B. In our modeling, substructure is not neccessary to exist to cause the observed flux ratio anomaly. This indicates the flux ratio anomaly in B1555+375 is resulted from the structure of lens galaxy itself, which is the edge-on disk seen in the SHARP infrared imaging. Our result is consistent with the conclusion from \citet{Xu14}. Their simulation gives a low probability on the hypothesis that substructure causing flux anomaly in B1555+375.

>>>>

\shorttitle{Gravitational Lens Modelling of Flux Ratio Anomalous System B1555+375}
\shortauthors{TBD}

@@

\title{Gravitational Lens Modelling of Flux Ratio Anomalous System B1555+375}
\author{TBD}

@@

\section{Lens Modelling}
To model B1555+375, we use the lens modelling code {\tt glafic}
\citep{Oguri}.  The inputs to the model are the observed image positions
and flux densities measured by the radio observations of \citet{Marlow}.
These authors present a singular isothermal ellipsoid (SIE) model that
provides the first fit to the image positions but
does not reproduce the strong flux ratio anomaly between components A and B.
(see Fig.6, Table 2 \& 3 in \citet{Marlow}). In K-band
image (Fig. 1, left), a recognizable edge-on disk is lie in the center
with position angle $~10$ degree. With this information, we model
B1555+375 with two models. The first model consists of an SIE bulge
and an exponential edge-on disk (SIE+Expdisk). The second model
consists of two SIE mass profiles (2-SIE), for bulge and disk
respectively. We assume that the lens galaxy has $z_{l}=0.5$ and the source has $z_s=1.5$. The full best-fit parameters are shown in Table 1. Both
of these models predict fairly matched results with the radio
observation. The comparison of observation and SIE+Expdisk result is
in Figure 2, Table 2 \& 3.
%These authors present a singular isothermal ellipsoid (SIE) model that
%provides an excellent fit to the image positions (?? IS THIS TRUE?--NO we get a better model result)

@@

Base on the fact that surface brightness is sensitive to perturbations in gravitational potential, flux ratio anomalies has been shown as one of the most effective methods to detect substructures \citep{Dalal2002} (more ref). Until now there are a dozen(?) known flux ratio anomalous systems and the number must increase in the future survey. Radio data provides reliable positions and fluxes of source for constraint and modelling because it avoids the problem of severe extinction and micro lensing from stars. On the other hand, optical or near infrared imaging also gives useful information about the lensing system. In the previous paper of SHARP, \citet{SHARP12} show that high resolution IR imaging improves the lens modelling. The lack of knowledge about lens galaxy, e.g. modelling with radio data alnog, may lead to an improper lens model.

@@

In sec. 2, we present new lens models of B1555+375 with a bulge and an edge-on disk. Our models better match to the radio image positions than in \citet{Marlow} and also explain the flux ratio anomaly between components A and B. In our modelling, substructure is not neccessary to exist to cause the observed flux ratio anomaly. This indicates the flux ratio anomaly in B1555+375 is resulted from the structure of lens galaxy itself, which is the edge-on disk seen in the SHARP infrared imaging. Our result is consistent with the conclusion from \citet{Xu14}. Their simulation gives a low probability on the hypothesis that substructure causing flux anomaly in B1555+375.
